---
title: "College Major and Income"
author: "Anshu"
date: "7/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(scales)
theme_set(theme_light())
```

```{r}
recent_grads <- read.csv('Data/recent-grads.csv')

majors_formatted <- recent_grads %>% 
  arrange(desc(Median)) %>% 
  mutate(Major = str_to_title(Major), #Using str_to_title to convert title case to sentence case 
         Major = fct_reorder(Major, Median)) #Reordering majors based on the descending values of their Median sal
  
```


### What are the most common majors?

What are the most common major categories (Eg: Business, Engineering, Arts)?

```{r}
majors_formatted %>% 
  count(Major_category, wt = Total, sort = T) %>%  #wt = total would multiply the no. of major categories by the number in each major
  mutate(Major_category = fct_reorder(Major_category, n)) %>% 
  ggplot(aes(Major_category, n, fill = Major_category)) + 
  geom_col() + 
  coord_flip() + 
  labs(x = "", 
       y = 'Total Number of Graduates', 
       title = 'The Most Common Major Categories') + 
  theme(legend.position = 'none') 

```


What are the most common *majors*? (Since there are 173, we aren't going to show them all)

```{r}
majors_formatted %>% 
  mutate(Major = fct_reorder(Major, Total)) %>% 
  arrange(desc(Total)) %>%
  head(20) %>% 
  ggplot(aes(Major, Total, fill = Major_category)) + 
  geom_col() + 
  coord_flip() + 
  labs(x = "", 
       y = 'Total Number of Graduates', 
       title = 'The Most Common Majors') +
  scale_y_continuous(labels = comma_format())
```



### What categories of majors earn the most? 

```{r}
majors_formatted %>% 
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category ,Median)) +
  geom_boxplot() + 
  scale_y_continuous(labels = dollar_format()) + 
  coord_flip() + 
  labs(title = 'Major Categories and their respective earnings',
       x = '',
       y = 'Median Salary in $')
```

```{r}
majors_formatted %>% 
  group_by(Major_category) %>%
  summarise(Median = median(Median)) %>% 
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category ,Median)) +
  geom_col() + 
  scale_y_continuous(labels = dollar_format()) + 
  coord_flip() + 
  labs(title = 'Major Categories and their respective earnings',
       x = '',
       y = 'Median Salary in $')
```


### What are the highest earning majors across all categories?

```{r}
majors_formatted %>%  
  filter(Sample_size >=100) %>% 
  head(20) %>%
  ggplot(aes(Major ,Median, color = Major_category)) +
  geom_point() + 
  expand_limits(y = 0) + #Including 0 in the Median Salary axis 
  geom_errorbar(aes(ymin = P25th, ymax = P75th)) + # Used to include the 25th and 75th percentiles 
  scale_y_continuous(labels = dollar_format()) + 
  coord_flip() + 
  labs(title = 'Highest Earning Majors',
       subtitle = 'Top 20 majors where more than 100 graduates were surveyed. Bars represent the 25th and 75th Percentiles',
       x = '',
       y = 'Median Salary in $')
```


### What are the lowest earning majors across all categories 

```{r}
majors_formatted %>%   
  tail(20) %>%
  ggplot(aes(Major ,Median, color = Major_category)) +
  geom_point() + 
  expand_limits(y = 0) + #Including 0 in the Median Salary axis 
  geom_errorbar(aes(ymin = P25th, ymax = P75th)) + # Used to include the 25th and 75th percentiles 
  scale_y_continuous(labels = dollar_format()) + 
  coord_flip() + 
  labs(title = 'Lowest Earning Majors',
       subtitle = 'Top 20 majors where more than 100 graduates were surveyed',
       x = '',
       y = 'Median Salary in $')
```


### To study the sample size of different majors 


```{r}
majors_formatted %>% 
  ggplot(aes(Sample_size, Median)) +
  geom_point() + 
  geom_text(aes(label = Major), check_overlap = T, vjust = 1, hjust = 1) + # To add text to the points based on the majors
  scale_x_log10() + 
  scale_y_continuous(labels = dollar_format())
```

